\section{TP-CF-002 --- Cold-flow \#2}

\begin{tabular}{@{}ll@{}}
\textbf{ID:} & TP-CF-002 \\
\textbf{Status:} & Pass \\
\textbf{Date / site:} & 14.07.2026 \\
\textbf{Test lead:} & Jan Sacharuk \\
\textbf{RSO:} & \todo{} \\
\textbf{Prerequisite:} & \todo{TP-CF-001 Pass / waiver ID} \\
\end{tabular}

\subsection*{Plan}

\paragraph{Objective}
\todo{e.g.\ Repeat / confirm cold-flow sequence after changes from CF-001;
close ENG-004 / GSE-001.}

\paragraph{Configuration}
\begin{itemize}
  \item Hardware: \todo{vehicle / stand article, GSE rev, instrumentation}
  \item Software / FC: \todo{N/A or version}
  \item Propellant / media: \todo{what is flowing; igniter safed?}
  \item \textbf{Hardware:} Test Box v0.1 (Engine Board V2 SN 2; Engine Board V2 SN 1; Raspberry pi 5)
  \item \textbf{Software:} \href{https://github.com/Simba-Avionic/srp/releases/tag/v1.2.0}{srp v1.2.0}
  \item \textbf{Control Device:} srp-app
\end{itemize}

\paragraph{Procedure}
\todo{Step list, or ``follow CONOPS cold-flow timeline + checklist X''.}

\paragraph{Success criteria}
\begin{itemize}
  \item \todo{No leaks at pressure P for t seconds}
  \item \todo{Valve sequence timing within \ldots}
  \item \todo{Complete log / photos}
\end{itemize}

\paragraph{Failure / abort criteria}
\begin{itemize}
  \item \todo{Any leak in hot zone $\rightarrow$ HOLD / vent / abort}
  \item \todo{Lost GSE link $\rightarrow$ abort to safe}
\end{itemize}

\paragraph{SRD IDs verified}
\todo{ENG-004, GSE-001, \ldots}

\paragraph{Hazards / safing}
\todo{Zones, PPE, abort card, wait times.}

\subsection*{Report}

\paragraph{Outcome}
Pass

\paragraph{Results}
\todo{Pressures, timings, compared to success criteria.}

\paragraph{Plots / data}
\todo{Path to CSV / figures; or \texttt{\textbackslash includegraphics}.}

\paragraph{Photos}
\todo{Setup, anomalies, post-test state.}

\paragraph{Anomalies}
\todo{None / list with severity.}

\paragraph{Conclusions / follow-ups}
\todo{Proceed to SF? Retest? Design / CONOPS change?}
