\section{Static fire}

\guidance{Static fire = engine ignition on the stand (vehicle / engine
restrained). Enter only after a successful cold-flow (or a written waiver
recorded here).}

\subsection{Goal and success criteria}

\begin{itemize}
  \item \textbf{Goal:} \todo{e.g.\ nominal burn X\,s, pressure/thrust data, no
    critical damage}
  \item \textbf{Full success:} \todo{}
  \item \textbf{Partial success:} \todo{e.g.\ ignition OK, early cutoff}
  \item \textbf{Failure:} \todo{misfire, hard start, fire, data loss}
\end{itemize}

\subsection{Hardware configuration}

\todo{Engine on stand / in vehicle? Load cell? Shields? Igniter?
Telemetry / DAQ? What is armed only in armed mode?}

\subsection{Crew and zones}

\todo{Minimum staffing; who holds abort; cold-area distance from the pad.}

\subsection{Go / no-go before static fire}

\noindent\begin{tabularx}{\linewidth}{@{}c X c@{}}
\toprule
\textbf{\#} & \textbf{Condition} & \textbf{GO?} \\
\midrule
1 & Cold-flow passed / waiver written & \todo{} \\
2 & \todo{stand, restraint, range clear} & \todo{} \\
3 & \todo{DAQ / TM live, igniter continuity} & \todo{} \\
4 & \todo{weather / wind / permits} & \todo{} \\
5 & \todo{extinguishers, RSO, misfire plan briefed} & \todo{} \\
\bottomrule
\end{tabularx}

\subsection{Static-fire timeline}

\noindent\begin{tabularx}{\linewidth}{@{}l l X l@{}}
\toprule
\textbf{Phase} & \textbf{Time} & \textbf{Action} & \textbf{Lead} \\
\midrule
Setup / integration & T$-$\,? & install, checks, dry run without igniter & \todo{} \\
Fueling & T$-$\,? & fill + press, personnel outside hot & \todo{} \\
Countdown & T$-$\,? & arming, final go/no-go & \todo{} \\
Burn & T$+$\,0 & ignition $\rightarrow$ burn $\rightarrow$ cutoff & --- \\
Safing & T$+$\,? & wait time, vent, approach & \todo{} \\
Inspection / debrief & T$+$\,? & damage, data, packing decision & \todo{} \\
\bottomrule
\end{tabularx}

\subsection{Step-by-step scenario}

\begin{enumerate}[leftmargin=*]
  \item \todo{Setup --- \ldots}
  \item \todo{Dry-run countdown --- \ldots}
  \item \todo{Fueling --- \ldots}
  \item \todo{Final go/no-go --- Launch Lead + RSO}
  \item \todo{Arming --- \ldots}
  \item \todo{Ignition / burn --- \ldots}
  \item \todo{Misfire wait (if no ignition) --- \ldots}
  \item \todo{Safing + inspection --- \ldots}
\end{enumerate}

\subsection{Typical static-fire contingencies}

\begin{itemize}
  \item \textbf{Misfire:} \todo{wait time, who approaches, igniter handling}
  \item \textbf{Hard start / overpressure:} \todo{abort, safing, evacuation}
  \item \textbf{Pad fire:} \todo{see safety + abort card}
  \item \todo{\ldots}
\end{itemize}
