\section{On-site plan (day by day)}

\guidance{Spell out each day at the range / competition: day goal, key time
blocks, evening go/no-go. Adjust the number of days to the real schedule.}

\subsection{Day overview}

\noindent\begin{tabularx}{\linewidth}{@{}l l X l@{}}
\toprule
\textbf{Day} & \textbf{Date} & \textbf{Day goal} & \textbf{Lead} \\
\midrule
D0 --- arrival & \todo{} & transport, check-in, partial unload & \todo{} \\
D1 --- setup & \todo{} & camp / GSE setup, organizer inspections & \todo{} \\
D2 --- readiness & \todo{} & integration, dry run, cold checks & \todo{} \\
D3 --- flight window & \todo{} & fueling, countdown, flight, recovery & \todo{} \\
D4 --- pack-up & \todo{} & teardown, debrief, departure & \todo{} \\
\bottomrule
\end{tabularx}

\todo{Add / remove days (e.g.\ on-site SF day, weather reserve day).}

\subsection{D0 --- arrival and check-in}

\begin{itemize}
  \item \todo{Departure time / ETA}
  \item \todo{Organizer check-in --- who goes, which documents}
  \item \todo{What unloads immediately vs.\ stays in the vehicle}
  \item \textbf{Evening go/no-go:} \todo{can D1 start with setup?}
\end{itemize}

\subsection{D1 --- on-site setup}

\begin{itemize}
  \item \todo{Tent / table / power / radio setup}
  \item \todo{Post-transport vehicle inspection}
  \item \todo{Meet RSO / organizers --- zones, windows, rules}
  \item \todo{Map: pad vs.\ camp vs.\ recovery}
  \item \textbf{Evening go/no-go:} \todo{}
\end{itemize}

\subsection{D2 --- readiness (integration / dry run)}

\begin{itemize}
  \item \todo{Subsystem integration, continuity, TM}
  \item \todo{Dry-run countdown \emph{without} propellant}
  \item \todo{Confirm roles and abort cards}
  \item \todo{Weather forecast for the flight window}
  \item \textbf{Evening go/no-go for fueling / flight:} \todo{}
\end{itemize}

\subsection{D3 --- flight day (detailed timeline)}

\guidance{Core of launch day. Relative times (T$-$ / T$+$).}

\noindent\begin{tabularx}{\linewidth}{@{}l l X l@{}}
\toprule
\textbf{Phase} & \textbf{Time} & \textbf{What happens} & \textbf{Lead} \\
\midrule
Morning briefing & T$-$\,? & weather, roles, day go/no-go & \todo{} \\
Pad setup & T$-$\,? & rail, GSE, radio, power & \todo{} \\
Integration / checks & T$-$\,? & checklists, dry leak-check & \todo{} \\
Fueling & T$-$\,? & propellant, press, personnel clear & \todo{} \\
Countdown & T$-$\,? & arming, final go/no-go, igniter & \todo{} \\
Flight & T$+$\,0 & launch, boost, coast, apogee, deploy & --- \\
Recovery & T$+$\,? & tracking, search, secure vehicle & \todo{} \\
Pad pack-up & T$+$\,? & GSE teardown, log, photos & \todo{} \\
Debrief & T$+$\,? & what went wrong, data, decisions & \todo{} \\
\bottomrule
\end{tabularx}

\subsubsection{Flight-day phase details}

\paragraph{Move to pad / setup}
\todo{Order; safe area vs.\ pad.}

\paragraph{Integration and pre-flight checks}
\todo{Checks before propellant.}

\paragraph{Fueling}
\todo{Who stands where; when the zone is hot; ``tanking complete'' criterion.}

\paragraph{Countdown}
\todo{Arming $\rightarrow$ ignition sequence; who calls GO; when abort is allowed.}

\paragraph{Flight (nominal)}
\todo{Lift-off $\rightarrow$ burnout $\rightarrow$ apogee $\rightarrow$
deploy $\rightarrow$ landing --- operationally.}

\paragraph{Recovery}
\todo{Tracking; who goes into the field; when approach is allowed.}

\subsection{D4 --- pack-up and departure}

\begin{itemize}
  \item \todo{Camp teardown / site return}
  \item \todo{Inventory vs.\ packing list}
  \item \todo{What returns for failure analysis}
  \item \todo{Written debrief (1 page) before departure}
\end{itemize}

\subsection{Reserve / slip day}

\todo{What you do if weather / pad / organizers shift the window:
which day becomes flight day, what is dropped, minimum dry run next day.}
