\section{Department requirements}

\guidance{One section per department. Keep requirements measurable.
Interfaces and diagrams $\rightarrow$ SAD; procedures $\rightarrow$ CONOPS /
Test Plan.}

\subsection{Engine}

\guidance{Engine department owns the propulsion system: chamber, injector,
ignition, and typically onboard tanks / feed hardware that delivers
propellant to the engine. Coordinate remotely actuated valves with GSE.}

\noindent\begin{tabularx}{\linewidth}{@{}l X c c l@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Pri.} & \VVHeader & \textbf{Owner} \\
\midrule
ENG-001 & Propellant combination shall be \todo{fuel / oxidizer}
  (change requires SRD approval). & Must & I & \todo{} \\
ENG-002 & Engine shall deliver thrust / burn time of
  \todo{T\,N for t\,s} (or performance envelope). & Must & T & \todo{} \\
ENG-003 & Ignition reliability shall be demonstrated in static fire
  per CONOPS success criteria. & Must & T & \todo{} \\
ENG-004 & Onboard feed / tanks shall support cold-flow and flight fueling
  without leaks at operating pressure \todo{P}. & Must & T & \todo{} \\
ENG-005 & MEOP / proof / burst factors for engine-side pressure hardware
  shall meet \todo{team safety standard / code}. & Must & A/T & \todo{} \\
ENG-006 & Engine-side valves required for hot/fueled ops shall be remotely
  operable via GSE. & Must & D/T & \todo{} \\
ENG-007 & \todo{Cutoff / abort / residual dump capability if any.} & \todo{} & \todo{} & \todo{} \\
\bottomrule
\end{tabularx}

\subsection{Aerostructure}

\noindent\begin{tabularx}{\linewidth}{@{}l X c c l@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Pri.} & \VVHeader & \textbf{Owner} \\
\midrule
AERO-001 & Airframe shall survive nominal flight loads with factor of safety
  \todo{FoS}. & Must & A/T & \todo{} \\
AERO-002 & Engine / tank mounts shall carry static-fire and flight loads. & Must & A/T & \todo{} \\
AERO-003 & Rail buttons / guides shall be compatible with
  \todo{rail type}. & Must & I & \todo{} \\
AERO-004 & Outer mold line / fin set shall provide static margin
  $\geq$\,\todo{Z}\,cal (with Simulations). & Must & A & \todo{} \\
AERO-005 & \todo{Additional aerostructure req.\ (mass budget share, integration).} & \todo{} & \todo{} & \todo{} \\
\bottomrule
\end{tabularx}

\subsection{Avionics}

\noindent\begin{tabularx}{\linewidth}{@{}l X c c l@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Pri.} & \VVHeader & \textbf{Owner} \\
\midrule
AV-001 & Flight computer shall detect apogee / deploy events per recovery
  requirements. & Must & T & \todo{} \\
AV-002 & Telemetry shall be live to the ground station from T$-$\,\todo{} through
  \todo{landing / loss of signal criteria}. & Must & T & \todo{} \\
AV-003 & Arming shall require an explicit, reversible action distinct from
  power-up (CONOPS armed mode). & Must & D & \todo{} \\
AV-004 & Onboard power shall last $\geq$\,\todo{t}\,min in the worst-case
  timeline (pad hold + flight + recovery search). & Must & T/A & \todo{} \\
AV-005 & \todo{Recording / backup data / sensor suite requirements.} & \todo{} & \todo{} & \todo{} \\
\bottomrule
\end{tabularx}

\subsection{Recovery}

\noindent\begin{tabularx}{\linewidth}{@{}l X c c l@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Pri.} & \VVHeader & \textbf{Owner} \\
\midrule
REC-001 & Recovery system shall limit descent rate to $\leq$\,\todo{v}\,m/s
  at landing. & Must & A/T & \todo{} \\
REC-002 & Deployment shall occur at / after apogee within
  \todo{timing / altitude} criteria. & Must & T & \todo{} \\
REC-003 & Vehicle shall be trackable to the expected landing area
  (\todo{radio / GPS / visual}). & Must & T/D & \todo{} \\
REC-004 & \todo{Dual-deploy / redundancy if required.} & \todo{} & \todo{} & \todo{} \\
\bottomrule
\end{tabularx}

\subsection{Simulations}

\guidance{Simulations does not fly hardware, but owns analyses that
\emph{close} mission and vehicle requirements before flight / SF.}

\noindent\begin{tabularx}{\linewidth}{@{}l X c c l@{}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Pri.} & \VVHeader & \textbf{Owner} \\
\midrule
SIM-001 & A trajectory / performance model shall predict apogee for the
  baseline vehicle within \todo{tolerance} of MIS-001 before flight. & Must & A & \todo{} \\
SIM-002 & Stability / aero analysis shall confirm AERO-004 (static margin)
  for the as-built mass properties. & Must & A & \todo{} \\
SIM-003 & Structural / loads analysis shall support AERO-001 / AERO-002
  with documented assumptions. & Must & A & \todo{} \\
SIM-004 & Simulations shall deliver pre-flight / pre-SF prediction packages
  used in go/no-go (CONOPS). & Should & I & \todo{} \\
SIM-005 & \todo{CFD / thermal / other analysis requirements if needed.} & \todo{} & \todo{} & \todo{} \\
\bottomrule
\end{tabularx}
